\centering DAOSYS: Smart DAO Protocol for Decentralized Finance

### 2022-09-23 latex/whitepaper/article.tex
appendix B

\begin{itemize}
\item \textbf{Block time:} 150 seconds
\item \textbf{Halving interval:} 210240 (1 year)
\item \textbf{Base Rewards:}  96.25 SYS per block deflated 5 percent every 210240 blocks
\item \textbf{NEVM Rewards:}  10.55 SYS per block (not deflated). EIP1559 model
\item \textbf{Governance Proposals:}  10 percent of Base Rewards paid out every 17520 blocks (1 month)
\item \textbf{Miner/Masternode Subsidy:}  90 percent of Base Rewards. 25 percent of this value goes to miner, 75 percent of this value goes to masternode
\item \textbf{Masternode Minimum Subsidy:} 5.275 SYS (can not go below this amount even accounting for deflation)
\item \textbf{Masternode collateral requirement:} 100,000 SYS
\item \textbf{Masternode seniority}: 35 percent increase after 210240 blocks (1 year), 100 percent increase after 525600 blocks (2.5 years)
\end{itemize}
Using the rule set described in the above specifications, we determine the Masternode rewards using the following relationship: 
\begin{equation*}
MN_{Rewards} = (Blocks_{Num}) (Coins_{New}) \left(\frac{Nodes_{Num}}{Supply_{New}}\right)
\end{equation*}
where current supply is calculated via the following:
\begin{equation*}
Supply_{New} = Supply + Coins_{New} - Transaction Fee 
\end{equation*}
and where transaction fees were calculated in accordance to Section \ref{appendix:tx_fee_burn}. Using Masternode returns, we calculated the USD value using Monte Carlo price projections as per Section \ref{appendix:monte_carlo}. Final total returns were determined via the following: 
\begin{equation*}
Total_{Rewards} = MN_{Rewards} + DAOSYS_{Rewards} 
\end{equation*}

>>>>

\begin{itemize}
\item \textbf{Block time:} 150 seconds
\item \textbf{Halving interval:} 210240 (1 year)
\item \textbf{Base Rewards:}  96.25 SYS per block deflated 5 percent every 210240 blocks
\item \textbf{NEVM Rewards:}  10.55 SYS per block (not deflated). EIP1559 model
\item \textbf{Governance Proposals:}  10 percent of Base Rewards paid out every 17520 blocks (1 month)
\item \textbf{Miner/Masternode Subsidy:}  90 percent of Base Rewards. 25 percent of this value goes to miner, 75 percent of this value goes to masternode
\item \textbf{Masternode Minimum Subsidy:} 5.275 SYS (can not go below this amount even accounting for deflation)
\item \textbf{Masternode collateral requirement:} 100,000 SYS
\item \textbf{Masternode seniority}: 35 percent increase after 210240 blocks (1 year), 100 percent increase after 525600 blocks (2.5 years)
\end{itemize}
Using the rule set described in the above specifications, we determine the Masternode rewards using the following relationship: 
\begin{equation*}
MN_{Rewards} = (Blocks_{Num}) (Coins_{New}) \left(\frac{Nodes_{Num}}{Supply_{New}}\right)
\end{equation*}
where current supply is calculated via the following:
\begin{equation*}
Supply_{New} = Supply_{Prev} + Coins_{New} - Fee_{TX} 
\end{equation*}
and $Fee_{TX}$ is calculated in accordance to Section \ref{appendix:tx_fee_burn}. Using Masternode returns, we calculated the USD value using Monte Carlo price projections as per Section \ref{appendix:monte_carlo}. Final total returns were determined via the following: 
\begin{equation*}
Total_{Rewards} = MN_{Rewards} + DAOSYS_{Rewards} 
\end{equation*}
